Nowcasting Covid-19 statistics reported with delay: a case-study of Sweden

### 2021-06-07 output/paper/paper.tex
Updates from Overleaf

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{plots/latest_prediction}
    \caption{Swedish Covid-19 deaths as of 2020-06-04 and model predictions}
    \label{fig:latest_prediction}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{plots/lag_prediction_by_date}
    \caption{Model accuracy over time for four dates, compared to benchmark}
    \label{fig:four_dates}
\end{figure}

Figure~\ref{fig:model_metrics} shows model performance compared to the benchmark for three difference performance metrics. All three graphs are based on predictions of reported deaths within 14 days, and show how performance increases as more data has been reported. Each data point is the average of all dates where predictions can be evaluated. SCRPS is a measure of accuracy that rewards precision, it is a proper scoring rule like the continuous probability rank score or the Brier score (see definition in Appendix) \citep{bolin2019scale}. The central plot shows the width of the prediction intervals, and the rightmost one the proportion of PI\'s that cover the true value.

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{plots/latest_prediction}
    \caption{Swedish Covid-19 deaths as of 2020-06-04 and model predictions}
    \label{fig:latest_prediction}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\textwidth]{plots/lag_prediction_by_date}
    \caption{Model accuracy over time for three randomly chosen dates, compared to the benchmark model}
    \label{fig:four_dates}
\end{figure}

Figure~\ref{fig:model_metrics} shows model performance compared to the benchmark for three difference performance metrics. All three graphs are based on predictions of reported deaths within 14 days, and show how performance increases as more data has been reported. Each data point is the average of all dates where predictions can be evaluated. CRPS is a measure of accuracy that rewards precision, it is a proper scoring rule like the continuous probability rank score or the Brier score (see definition in Appendix) \citep{bolin2019scale}. The central plot shows the width of the prediction intervals, and the rightmost one the proportion of PI\'s that cover the true value.
